---
title: "JSON Viewer"
format: 
  html:
    page-layout: full
---

In this page you will find the Dataset-JSON Viewer Shiny application authored by Sebastià Barceló & Hugo Signol, originally developed for the 3rd [CDISC Dataset-JSON Viewer Hackathon](https://www.linkedin.com/pulse/results-from-cosa-dataset-json-viewer-hackathon-sam-hume-kgbge) for which it won an honorable mention. This is a powerful and user-friendly Shiny application for exploring and analyzing JSON data sets with interactive features and comprehensive data visualization capabilities. For additional details, please refer to the [usage guide](https://github.com/sbarcelo777/Dataset-JSON-hackathon/blob/master/README.md#-user-guide) from the project's [GitHub repository](https://github.com/sbarcelo777/Dataset-JSON-hackathon/).

The specific application below is based on a fork of the original application with selected example JSON data files pre-loaded in the user interface for convenience. The repository for this version of the app can be found [here](https://github.com/rpodcast/Dataset-JSON-hackathon).

```{r}
#| echo: FALSE
#| message: FALSE
#| eval: false

library(htmltools)
source("R/create_shinylive_url.R")
# Replace with your desired repository owner and name
owner <- "sbarcelo777"
repo <- "Dataset-JSON-hackathon" 
# Download and extract the repository to a temporary directory
repo_path <- download_github_repo(owner, repo)
# List files in the extracted repository (optional)
if (FALSE){
  if (!is.null(repo_path) && dir.exists(repo_path)) {
    cat("Files in the repository:\n")
    print(list.files(repo_path, recursive = TRUE))
  }
}
shinylive_url <- url_encode_dir(repo_path, mode = "app", exclude = "rsconnect/|html|svg")
```

It is embedded below with the help of [{shinylive}](https://shiny.posit.co/py/docs/shinylive.html) and WebAssembly. The app should load below; otherwise, please click [here](https://rpodcast.github.io/Dataset-JSON-hackathon/).

```{r}
#| echo: FALSE
#| message: FALSE

htmltools::tags$iframe(
  title = "JSON Viewer",
  src = "https://rpodcast.github.io/Dataset-JSON-hackathon/",
  style = "width: 100%; height: 600px; border: none;",
  allowfullscreen = FALSE
)
```
